---
title       : Car Payment Calculator
subtitle    : simple car payment calculator
author      : Carlos Santillan
job         : 
framework   : io2012        # {io2012, html5slides, shower, dzslides, ...}
highlighter : highlight.js  # {highlight.js, prettify, highlight}
hitheme     : tomorrow      # 
widgets     : []            # {mathjax, quiz, bootstrap}
mode        : selfcontained # {standalone, draft}
knit        : slidify::knit2slides
---


```{r formula-cacl, echo=FALSE }

CalculatePaymentAmount<-function(P,n, R) {
    r <- (R/12)/100
    N <- n
    M <- (P*r)/(1-(1+r)^(-n))
    monthPay <- M
    totalPay <- M*n -P

    return (c(monthPay,totalPay))
}

```

## Car Payment Calculator

### Know what the estimate monthly car payment will be before you buy

* How much vehicle can you afford?
* What impact will a downpayment have on monthy payment?
* Shop around for better interest Rate

---

## Car Sale price

Make sure you research the car you are interested in buying and shop around.
The same car may be found at different dealers at significant discount


```{r carsale, echo=FALSE }
 p1 <- CalculatePaymentAmount(25000,60,6)[1]
 p2 <- CalculatePaymentAmount(23000,60,5)[1]
```

The payment amount for a 5% interest load on a vehicle that costs $25,000.00 over 60 months will be `r format(p1 ,digits=2,nsmall=2)` , if you can find same vehicle for $23,000.00 the payment will be `r format(p2,digits=2,nsmall=2)` a saving of `r format( p1-p2,digits=2,nsmall=2)` a month






--- 

## Trade in Value

 * Check sites such as [Kelly Blue Book](http://www.kbb.com/) to estimate the value of your trade in
 
 * Car wash/Detail could add value to car

--- 

## Down Payment

```{r downpayment, echo=FALSE }
 carcost <- 25000
 downpayment <-3000
 downpayment2 <-4000
 pNodown <- CalculatePaymentAmount(carcost,60,5)[1]
 pwDown <- CalculatePaymentAmount(carcost-downpayment,60,5)[1]
 pwDown2 <- CalculatePaymentAmount(carcost-downpayment2,60,5)[1]
 
```

 Saving for a down payment could save you many
 Try different combinations of down payment to see how it affects your car Payment
 
 * With no down payment a $25,000.00 car 5 year, 5 % car will have a cost of $ `r format(pNodown,digits=2,nsmall=2)`.
 
 * With $3,000 down payment a $25,000.00 car 5 year, 5 % car will have a cost of $ `r format(pwDown,digits=2,nsmall=2)`
 
 * With $5,000 down payment a $25,000.00 car 5 year, 5 % car will have a cost of $ `r format(pwDown2,digits=2,nsmall=2)`

---

## Interest Rate


```{r carInterest, echo=FALSE }
 r1 <- CalculatePaymentAmount(25000,60,4)[1]
 r2 <- CalculatePaymentAmount(25000,60,5)[1]
 total1 <- CalculatePaymentAmount(25000,60,4)[2]
 total2 <- CalculatePaymentAmount(25000,60,5)[2]
```

 Get preapproved for your loan from your bank or a credit union.
 
 Dealers may have their own financing options but they may not be the best deal. 
 A good intest rate could save you thousands over the life of the loan
 
 * $25,000.00 car 5 year, 5 % car will have a monthly payment of `r format(r1,digits=2,nsmall=2)`, and total cost of loan of `r format(total1,digits=2,nsmall=2)`
 * $25,000.00 car 5 year, 5 % car will have a monthly payment of `r format(r2,digits=2,nsmall=2)`, and total cost of loan of `r format(total2,digits=2,nsmall=2)`

--- 


## Term

60 months (5 year) loans may help you lower the monthly payment, but you will pay more in interest.



```{r Term, echo=FALSE }
 termp1 <- CalculatePaymentAmount(25000,60,5)[1]
 termp2 <- CalculatePaymentAmount(23000,48,5)[1]
```

* $25,000.00 car 5 year, 5 % car will have a monthly payment of `r format(termp1,digits=2,nsmall=2)`
 
* $25,000.00 car 4 year, 5 % car will have a monthly payment of `r format(termp2,digits=2,nsmall=2)`



---

